\documentclass[12pt,letterpaper]{article}
\usepackage{amsmath} % just math
\usepackage{amssymb} % allow blackboard bold (aka N,R,Q sets)
\usepackage{ulem}
\usepackage{graphicx}
\usepackage{float}
\linespread{1.6}  % double spaces lines
\usepackage[left=1in,top=1in,right=1in,bottom=1in,nohead]{geometry}
\setcounter{section}{3}
\begin{document}
\begin{flushright}
\end{flushright}
\begin{flushleft}
\textbf{Eric Zounes} \\
\today \\ 
Sec 3.1: 10*, 15ab \\
Sec 3.2: 3, 9*, 13 \\
Sec 3.3: 8* \\
Sec 3.4: 7, 8, 9*, 13, 14 \\
Sec 3.5: 7*, 8 \\
\end{flushleft}
\subsection{The Bisection Method} 
	\begin{enumerate} 
		\item[10.] Consider the equation $e^{-x} = sin(x)$. Find an interval $[a,b]$ that contains the smallest positive root. Estimate the number of midpoints c needed to obtain an approximate root that is accurate within an error tolerance of $10^{-10}$. \\
        $| \alpha - \epsilon_{n} | \leq \frac{1}{2^{n}}(b - a)$ \\
        $a = 0, b = 1$ \\
        $10^{-10} \leq \frac{1}{2^{n}}(1 - a) = \frac{1}{2^{n}}$ \\
        $\frac{1}{10^{-10}} \leq \frac{1}{2^{n}}$ \\
        $2^{n} \geq 10^{10}$ \\
        If we take the log of both sides we obtain \\
        $n \geq log_{2}(10^{10}) = 33.21$ \\ 
	\end{enumerate} 
\subsection{Newton's Method}
	\begin{enumerate} 
		\item[9.] Derive formula $(3.15)$. Using it, show $Rel(x_{n}) = [Rel(x_{0})]^{2^{n}}$ \\
			We want to derive $Rel(x_{n+1}) = [Rel(x_{n})]^{2}, n \geq 0$ where \\
			$Rel(x_{n}) = \frac{\alpha - x_{n}}{\alpha}$ \\   
            $Rel(x_{n+1}) = 1 - bx_{n+1}$ \\

			
	\end{enumerate} 
			
\subsection{Secant Method} 
	\begin{enumerate} 
		\item[8.] Write formula $(3.28)$ as $\alpha - x_{n+1} \approx M(\alpha - x_{n})(\alpha - x_{n-1}), n \geq 0$ \\
		with M defined in $3.21)$. Then multiply both sides by M, obtaining \\
		$| M(\alpha - x_{n+1}) | \approx | M(\alpha - x_{n}) | | M(\alpha - x_{n-1})|$ \\
		Let $B_{n} = | M(\alpha - x_{n}) |, n \geq 0$. To have $x_{n}$ converge to $\alpha$, we must have $B_{n}$ converge to 0. The above formula yields \\
		$B_{n+1} \approx B_{n}*B_{n-1}$ \\
		For simplicity, assume $B_{0} = B_{1} = \delta$ \\
		\begin{enumerate}
			\item Compute approximate values of $B_{2}, B_{3}, B_{4}, B_{5}, B_{6}, B_{7}$ in terms of $\delta$ \\
			$B_{2} = \delta^{2}$ \\
			$B_{3} = \delta^{2}*\delta^{1} = \delta^{3}$ \\
			$B_{4} = \delta^{3}*\delta^{2} = \delta^{5}$ \\
			$B_{5} = \delta^{5}*\delta^{3} = \delta^{8}$ \\
			$B_{6} = \delta^{8}*\delta^{5} = \delta^{13}$ \\
			$B_{7} = \delta^{13}*\delta^{8} = \delta^{21}$ \\
			
		\item If we write $B_{n} = \delta^{q_{n}}, \geq 0$, give a formula for $q_{n+1}$ in terms of $q_{n-1}$ and $q_{n}$. What are $q_{0}$ and $q_{1}$? \\
			$q_{n+1} = q_{n} + q_{n-1},$    $q_{0} = q_{1} = 1$ \\
			This equation represents a recurrence relation between $q_{n+1}, q_{n},$ and $q_{n-1}$. \\
			\item Experimentally, confirm that \\
			$q_{n} \approx \frac{1}{\sqrt{5}}r^{n+1} = \frac{1}{\sqrt{5}}(1.618)^{n+1}$ \\
			for larger values of $n$, say, $n \geq 4$. The number $r$ was used in $(3.30)$. The numbers \{$q_{n}$\} are called Fibonacci numbers. The number $r$ is called the golden mean.
			\item Using $(c)$, show that \\
			$\frac{B_{n+1}}{B_{n}^{r}}$ \\
			is approximately constant. Find the constant. This result can be used to construct a proof of $(3.30)$ 
			The ratio between each $n$ and $n+1$ Fibonacci number is $r$ and equal to our golden mean. For example: \\
			$\frac{B_{4+1}}{B_{4}} = 8.02391/4.95915 $ is $\approx 1.618$. 
		\end{enumerate} 
	\end{enumerate} 
\subsection{Fixed Point Iteration}
	\begin{enumerate}
		\item[9.] Consider the rootfinding problem $f(x) = 0$ with root $\alpha$, with $f'(x) \neq 0$. Convert it to the fixed-point problem \\
		$x = x + cf(x) \equiv g(x)$ \\
        Our equation is \\
        $x^{3} - 5 = 0$ \\
        With $x_{n+1} = x_{n} + cf(x_{n})$ we can define \\
        $c = \frac{1}{f'(x)}$ \\
        $c = \frac{1}{3x^{2}}$ \\ 
    \end{enumerate}  
\subsection{Ill-behaving Rootfinding Problems}
	\begin{enumerate}
		\item[7.] Consider the polynomial $f(x) = x^{5} - 300x^{2} - 126x + 5005,$ which has a root $\alpha = 5$. Also consider the perturbed function \\
		$F_{\epsilon}(x) = f(x) + \epsilon x^{5} = (1 + \epsilon)x^{5} - 300x^{2} - 126x + 5005$ \\
		with $\epsilon$ being a small number. Letting $\alpha(\epsilon)$ denote the perturbed root of $F_{\epsilon}(x) = 0$ corresponding to $\alpha(0) = 5$, estimate $\alpha(\epsilon) - 5$. Is finding $\alpha = 5$ for $f(x) = 0$ an unstable rootfinding problem? \\
		$\alpha(\epsilon) - 5 \approx 3125\epsilon,$ This problem is an unstable problem due to the large coefficient of $\epsilon$. \\ 
	\end{enumerate} 	
		
			
\end{document}
